\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\setlength{\footskip}{5pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\hypersetup{
  colorlinks=true,
  urlcolor=black
}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemDate}[3]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}{\textit{\small#3}}
  }
}

\newcommand{\resumeItemNoHeading}{\item\small\vspace{-2pt}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[3]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      {#1} \textit{#2} & \textit{\small #3}
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeSubItemDate}[3]{\resumeItemDate{#1}{#2}{#3}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large James Hurley} & \href{mailto:jhurley070@gmail.com}{jhurley070@gmail.com}  \href{tel:00353852428831}{+35385 242 8831}\\
  102 Rosemount Estate, Dundrum, Dublin 14 & \href{https://www.linkedin.com/in/jhurley1/}{linkedin.com/in/jhurley1/}  \href{https://www.github.com/jhurl3y/}{github.com/jhurl3y/}
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.surveymonkey.com}{SurveyMonkey}}{Dublin, Ireland}
      {Software Engineer}{Aug 2018 - Present}
      \resumeItemListStart
        \resumeItemNoHeading
          {Working as a key contributor in a high functioning growth team, liaising closely with product managers, designers and data analysts to enhance the SurveyMonkey product.}
        \resumeItemNoHeading
          {Developing full-stack customer facing in product features using React \& Python, touching multiple microservices. Consistently monitoring new feature rollout using A/B tests to gain insights \& metrics.}
        \resumeItemNoHeading
          {Maintaining and improving our internal A/B testing service used by multiple development teams across the company. Co-owner of the SurveyMonkey ads service used to promote features and advertise product updates.}
        \resumeItemNoHeading
          {Technical lead on various projects, writing tech specs and helping provide the technical direction to facilitate new requirements for experimentation. Writing unit tests and providing code reviews across multiple repositories.}
        \resumeItemNoHeading
          {Conducted many interviews for different software engineer roles for the payments \& growth teams.}
        \resumeItem
          {Technologies:}{ES6, React/Redux, Python, Pyramid, GraphQL, Docker, Jinja, Microservices, Webpack, pytest.}
      \resumeItemListEnd
    \resumeSubheading
      {\href{https://www.exordo.com}{Ex Ordo}}{Galway, Ireland}
      {Software Engineer}{Jun 2016 - Jul 2018}
      \resumeItemListStart
        \resumeItemNoHeading
          {Built new features, improved existing features both front-end and back-end. Desiged systems and owned projects from concept to completion. Pushed commits daily; hot-fixed critical issues; thoroughly tested code.}
        \resumeItemNoHeading
          {Managed releases through Alpha/Beta testing, ensured our product was of highest possible quality. Worked effectively with the customer support team; answered questions \& resolved issues across all platforms.}
        \resumeItem
          {Technologies:}{Padrino, Ruby, ActiveRecord, SCSS, HAML, Javascript, Backbone.js, Git, MySQL.}
      \resumeItemListEnd
    \resumeSubSubheading
      {Intern Software Engineer}{May 2015 - Sep 2015}
      \resumeItemListStart
        \resumeItemNoHeading
          {Developed various internal tools to help customer support to manage operations, merge duplicate user accounts and setup test conference instances with fake data. Built features to automate manual work for conference organisers, including a duplicate paper finder and a ready-to-print timetable export tool.}
      \resumeItemListEnd
    \resumeSubheading
      {\href{https://www.econiq.com}{Econiq}}{Galway, Ireland}
      {Intern Software Engineer}{May 2014 - Sep 2014}
      \resumeItemListStart
        \resumeItemNoHeading
          {Research internship related to JEE architecture and enterprise level web applications.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National University of Ireland, Galway}{Galway, Ireland}
      {BE in Electronic and Computer Engineering;  \textbf{1st Class Honours} (83/100)}{2012 -- 2016}
    \resumeSubheading
      {Yeats College, Galway}{Galway, Ireland}
      {Achieved maximum score in state examinations: \textbf{625 points} with 8 As.}{2010 -- 2012}
  \resumeSubHeadingListEnd

%-----------AWARDS-----------------
\section{Awards}
  \resumeSubHeadingListStart
    \resumeSubItemDate{ON Semiconductor Electronics Scholarship}
      {Awarded to three final year students nationally each year.}{Sep 2015.}
    \resumeSubItemDate{University Scholar}
      {Awarded title ‘University Scholar’ based on third year results.}{Sep 2015.}
    \resumeSubItemDate{Excellence scholarship}
      {Awarded university entrance scholarship based on Leaving Certificate results.}{Oct 2012.}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {Final Year Project:}{\href{https://github.com/jhurl3y/wheelchair-nav}{To design a GPS-based autonomous system for wheelchair users}}{Sep 2015 - April 2016}
      \resumeItemListStart
        \resumeItem{Technologies Used}
          {Android, Java, Google Maps API, Python, RFCOMM, UDP, Bluetooth, OpenCV, Control Systems, Kalman Filtering, Feature Detection and Optical Flow tracking.}
      \resumeSubHeadingListEnd
    \resumeProjectHeading
      {3rd Year Project:}{\href{https://www.youtube.com/watch?v=6YqNerpiGpM}{EngSoc Student Card Scanner}}{Sep 2014 - April 2015}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
 \section{Skills and Interests}
   \resumeSubHeadingListStart
     \resumeSubItem{Strong Technical Knowledge:}
       {Javascript, Python, Ruby, Java, React, Redux, Pyramid, Webpack, HTML, CSS, MySQL, Padrino, Active Record, Android, Docker, GraphQL, pytest, Jest, Pyramid, Git.}
     \resumeSubItem{Interests}
       {Web \& Mobile Development, System Design, Databases, Electronics, Computer Vision, Machine Learning.}
   \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
